Search for Spatially Extended \fermi-LAT Sources Using Two Years of Data

### 2011-11-09 extended_catalog/paper/extended_catalog.tex
adding everybodys changes

\begin{abstract}
Spatial extension is an important characteristic for correctly
associating LAT sources with their counterparts at other wavelengths
and for obtaining an unbiased model of their spectra.  We present a new
method for quantifying the spatial extension of sources detected by the Large
Area Telescope (LAT), the primary science instrument on the {\em \fermi
Gamma-ray Space Telescope} (\fermi).  We perform a series of Monte Carlo
simulations to validate this tool and calculate the LAT threshold for
detecting the spatial extension of sources.  We then test all sources
in the second \fermi-LAT catalog (2FGL) for extension. 
We report the
detection of seven spatially extended sources in addition to the twelve
spatially extended sources reported in 2FGL and two others studied
in dedicated publications.
\end{abstract}

@@

A number of astrophysical source classes including supernova remnants
(SNRs), pulsar wind nebulae (PWNe), molecular clouds, normal galaxies,
and galaxy clusters are expected to be spatially resolvable at
\gev energies.  Dark matter satellites are also hypothesized to
be spatially extended.  The Large Area Telescope
(LAT) on the {\em \fermi Gamma-ray Space Telescope} (\fermi) has
detected seven SNRs which are significantly extended
at \gev energies: 
W51C, W30, 
IC443, W28, W44, RX\,J1713.7$-$3946,
and the Cygnus Loop
\citep{w51c,w30_lat,ic443,w28,w44,rx_j1713_lat,cygnus_loop_lat}. In addition, 
three extended PWN have been detected: MSH\,15$-$52, Vela~X, and
HESS\,J1825$-$137 \citep{msh1552,velax,fermi_hess_j1825}. Two
nearby galaxies, the Large and Small Magellanic Clouds, and one
radio galaxy, Centaurus A, were spatially resolved at \gev energies
\citep{lmc,smc,cen_a_lat}.  A number of additional sources detected
at \gev energies are positionally coincident with sources that exhibit
extension at other wavelengths, large enough to be spatially
resolvable by the LAT at \gev energies.

The current generation of air Cherenkov detectors have
made it apparent that many sources can be spatially resolved
at even higher energies.
Most
prominent was a survey of the Galactic plane using the High Energy
Stereoscopic System (H.E.S.S) which reported 14 spatially extended
sources with extensions varying from $\sim0\fdg1$ to $\sim0\fdg25$
\citep{hess_plane_survey}.  In fact, within our Galaxy only very few
sources detected at \tev energies, most notably the $\gamma$-ray binaries
LS\,5039 \citep{HESSLS5039}, LS I+61$-$303 \citep{MAGICLSI, VERITASLSI},
HESS\,J0632+057 \citep{HESS0632}, and the Crab nebula \citep{crab_weekes},
have no detectable extension.  High-energy $\gamma$-rays from
these sources are produced by the decay of $\pi^0$s produced by hadronic
interactions with interstellar matter and by relativistic electrons
due to Inverse Compton (IC) scattering and Bremsstrahlung radiation.  
It is plausible that the \gev and
\tev emission from these sources originates from the same population of
high-energy particles and so at least some of these sources should be
detected at \gev energies.  Studying 
these \tev sources at \gev energies would help to
determine the emission mechanisms producing these high energy photons.

@@

Previous analysis of extended LAT sources was performed as dedicated
studies of individual sources so we expect that a systematic scan of
all LAT detected sources could uncover additional spatially extended
sources.  For these reasons, in Section~\ref{analysis_methods_section}
we present a new systematic method for analyzing spatially extended
LAT sources.  In Section~\ref{monte_carlo_validation}, we demonstrate
that this method can be used to test the statistical significance of the
extension of a LAT source and in Section~\ref{extension_sensitivity}
we calculate the LAT detection threshold to resolve the extension
of a source.  In Section~\ref{dual_localization_method}, we
study the ability of the LAT to distinguish between a spatially
extended source and the confusion of nearby point-like sources.
In Section~\ref{test_2lac_sources}, we further demonstrate that our
detection method does not misidentify point-like sources as being
extended by testing the extension of active galactic nuclei (AGN)
believed to be unresolvable.  In Section~\ref{validate_known},
we systematically reanalyze the twelve extended sources included
in 2FGL and in Section~\ref{systematic_errors_on_extension}
we describe a way to estimate systematic errors on the extension of a source.
In Section~\ref{extended_source_search_method}, we
describe a search for new spatially extended LAT sources. Finally,
in Section~\ref{new_ext_srcs_section} we present the detection of the
extension of nine spatially extended sources that were reported in 2FGL
but as being point-like.  Two of these sources have been previously analyzed in
dedicated publications.

@@

A new analysis tool has been developed to address the unique requirements
for studying spatially extended sources with the LAT.
The Poisson likelihood to find
the observing counts is maximized given a parametrized spatial and
spectral model of the source and its surrounding region.  The sky is
divided into cubes of space and energy using the healpix representation
of the sky \citep{healpix} and the likelihood is maximized over all bins
in a region.  The extension of a source can be modeled by a geometric
shape (e.g. a disk or a two-dimensional Gaussian) and the position, extension,
and spectrum of the source
can be simultaneously fit.

@@

The approach presented here is based on a second maximum likelihood
fitting package developed in the LAT Collaboration called \pointlike
\citep{first_cat,matthew_kerr_thesis}.  The choice to base the
spatial extension fitting on \pointlike rather than \gtlike was made
on considerations of computing time.  The \pointlike algorithm was
optimized for speed to handle larger numbers of sources efficiently,
which is important for our catalog scan and for being able
to perform large-scale Monte Carlo simulations to validate the analysis.
Details on the \pointlike package can be
found in \cite{matthew_kerr_thesis}.  We extended the code to allow a
simultaneous fit of the source extension together with the position and
the spectral parameters.

@@

We considered two different models that can be used to model the
surface brightness profile for extended sources, either a 2D Gaussian
profile
\begin{equation}\label{gauss_pdf}
  I_\text{Gaussian}(x,y)=\tfrac{1}{2\pi\sigma^2}\exp\left(-(x^2+y^2)/2\sigma^2\right)
\end{equation}
or a uniform surface brightness profile
\begin{equation}\label{disk_pdf}
  I_\text{disk}(x,y)=
  \begin{cases}
    \frac{1}{\pi\sigma^2} & x^2+y^2\le\sigma^2 \\
    0                      & x^2+y^2>\sigma^2.
  \end{cases}
\end{equation}
Although these shapes are significantly different, 
Figure~\ref{compare_disk_gauss} shows that their PDF 
are similar for a source that has a 
0\fdg5
radius
typical of LAT detected extended sources.
To
allow a valid comparison between the Gaussian and the uniform surface
brightness morphologies,
we define the source size 
as the radius containing
68\% of the intensity ($\rsixeight$).  $\rsixeight_\text{,Gaussian}=1.51\sigma$
and $\rsixeight_\text{,disk}=0.82\sigma$ where $\sigma$
is defined in Equation~\ref{gauss_pdf} and
Equation~\ref{disk_pdf} respectively.
For this example, $\rsixeight=0\fdg5$ so
$\sigma_\text{disk}=0.61\degree$ and 
$\sigma_\text{Gaussian}=0.33\degree$.

@@

It is impossible to discriminate with LAT data exclusively between a
spatially extended source and multiple point-like sources separated by
angular distances comparable to or smaller than the size of the LAT PSF.
To assess the plausibility of source confusion for situations
in which $\tsext>16$, we developed an algorithm in \pointlike to
simultaneously fit the position and spectrum of two point-like sources.

After simultaneously fitting the two positions and two spectra,
we define \tsinc as twice the increase in the log of the likelihood
fitting the region as two point-like sources compared to fitting the
region as one point-like source:
\begin{equation}
  \tsinc=2\log(\likelihood_\text{2pts}/\likelihood_\text{ps}).
\end{equation} 
For the following analysis of LAT data, \tsinc was computed
by fitting the spectra of the two point-like sources in \gtlike using the best fit positions
of the sources found by \pointlike.

@@

We assessed the power of the $\tsext>\tsinc$ test with a Monte Carlo
study.  We simulated one spatially extended source and fit it as both
an extended source and as two point-like sources using \pointlike.
We then simulated two point-like sources and fit them with the same two
hypotheses. By comparing the distribution of \tsinc and \tsext computed by
\pointlike for the two cases, we evaluated how good the $\tsext>\tsinc$
test is at rejecting the possibility of source confusion as well as how
likely it is to incorrectly reject that an extended source is spatially
extended.  All sources were simulated using the same time range as in
Section~\ref{extension_sensitivity} against a background 10 times the
isotropic background measured by EGRET, representative of the background
near the Galactic plane.

@@

The distributions also show that for simulated
extended sources with typical
sizes ($\sigma\sim0\fdg5$), one can often obtain almost as good 
an increase in likelihood
with two sources as with one extended source ($\tsinc\sim\tsext$).
This is because although
two point-like sources represent an incorrect spatial model, 
the two point-like sources have four additional degrees
of freedom (two spatial and two spectral parameters)
and can therefore easy model
the extended source and statistical fluctuations in the data.
This effect is most pronounced when using photons with energies between 1
\gev and 100 \gev where the PSF is even larger.  
On the other hand,
when testing the two simulated point-like sources for extension our test
found that \tsinc was larger than \tsext.
This is because the one additional extension parameter is less able to
model the second source or statistical fluctuations.
From this, we conclude that the $\tsext>\tsinc$ test is 
powerful at discarding cases in which the true emission is derived
from two point-like sources instead of from a spatially extended
source.

@@

To validate our method, we tested LAT sources associated with AGN for
extension.  \gev emission from AGN is believed to originate from the
cores of kiloparsec-scale jets of distant galaxies.  Therefore AGN are
not expected to be spatially resolvable by the LAT and provide a good
calibration source to demonstrate that our extension detection method
does not misidentify point-like sources as being extended.  We note that
megaparsec-scale $\gamma$-ray halos around AGNs have been hypothesized
to be resolvable by the LAT \citep{pair_halo_paper}. However, no such
halo has been discovered in the LAT data so far.

@@

We should clarify that the LAT PSF used in this study was determined
empirically by fitting the observed shape of bright AGN (see
Section~\ref{systematic_errors_on_extension}). Finding that the AGN we
test are not extended is not surprising.  This validation analysis is
not suitable to reject any hypotheses about the existence of megaparsec-scale
halos around AGN.

@@

We developed two criteria for estimating systematic errors
on the extension of the sources.
First, we estimated a systematic error due to
uncertainty in our knowledge of the LAT PSF.  
Before launch, the LAT PSF
was determined by detector simulations which were verified in accelerator
tests \citep{atwood_LAT_mission}. However, in-flight data revealed
a discrepancy above a few \gev in the PSF compared to the angular
distribution of photons from bright AGN \citep{lat_on_orbit_psf}.
Subsequently, the PSF was fit empirically to bright AGN and this
empirical parameterization is used in the P7\_V6 IRFs.  To account for
our uncertainty in our knowledge of the PSF, we refit our extended source
candidates using the pre-flight Monte Carlo representation of the PSF
and consider the difference in extension found using the two PSFs as a
systematic error on the extension of a source.  The same approach was used
in \cite{ic443}.  At high energies, we believe that our parameterization
of the PSF from bright AGN is substantially better than the Monte Carlo
representation of the PSF so this systematic error is conservative.

@@

We estimated a second systematic error on the extension of a source
due to uncertainty in our model of the Galactic diffuse emission by
using an alternative model which takes as input templates
calculated by
GALPROP\footnote{GALPROP is a software package for calculating the
Galactic $\gamma$-ray emission based on a model of cosmic-ray propagation
in the Galaxy \citep{galprop1998,galprop2011}. 
See also \url{http://galprop.stanford.edu/} for details.} 
but then fits each template locally in
the surrounding region.
The particular GALPROP model that was used as input is described in
the LAT analysis of the isotropic diffuse
emission \citep{isotropic_lat}.  
The intensities of various components
of the Galactic diffuse emission were fitted individually using a
spatial distribution of the intensities within the ROI as predicted by
the model.  We distinguished contributions from CR interactions with the
molecular hydrogen, the atomic+ionized hydrogen, residual gas traced
by dust \citep{isabelle_dark_gass}, and the interstellar radiation
field. We further split the contributions from interactions with molecular
and atomic hydrogen to the Galactic diffuse emission according to the
distance from the Galactic center in which they are produced. Hence, we
replaced the standard diffuse emission model by 18 individually fitted
templates to describe individual components of the diffuse emission.
A similar crosscheck was used in an analysis of RX\,J1713.7$-$3946 
by the LAT Collaboration \citep{rx_j1713_lat}.

@@

The best fit position of nearby point-like sources can be influenced by
the extended source and vice versa.  Similarly,
the best fit position of nearby point-like sources in 2FGL can be biased
by systematic errors at lower energies.
Therefore, after selecting the list of background sources, we iteratively
refit the position and spectrum of nearby background sources as well as
the position and extension of the analyzed spatially extended
sources until the overall fit globally converged.  For each extended
source, we will describe the position of any relocalized background
sources.

After obtaining the overall best fit positions and extensions of all
of the sources in the region using \pointlike, we refit the spectral
parameters of the region using \gtlike.  Using \gtlike, we obtained a
second measure of \tsext.  We only consider a source to be extended when
both \pointlike and \gtlike agree that $\tsext>16$. 
We further required that $\tsext>16$ using the alternate diffuse
model presented in section~\ref{systematic_errors_on_extension}.
We then replaced the spatially extended source with two point-like
sources and refit the position and spectrum of the
two point-like sources to calculate \tsinc.
We only consider a source to be spatially extended, instead of being
the result of confusion of two point-like sources, if $\tsext>\tsinc$.
As was shown in Section~\ref{dual_localization_method}, this test is
fairly powerful at removing situations in which the emission actually
originates from two distinct point-like sources instead of one spatially
extended source.  On the other hand, it is still possible that improved
observations could resolve additional structure or new sources that we are
currently not sensitive to. Considering the very complicated morphologies
of extended sources observed at other wavelengths and the high density
of possible sources that are expected to emit at \gev energies, it is
likely that in some of these regions further observations will resolve
that the emission is significantly more complicated than the simple
radially-symmetric uniform surface brightness profile that we assume.

@@

This source is in a region of remarkably complicated diffuse emission.
Even though it is $16\degree$ from the Galactic plane, this source is on
top of the core of the Ophiuchus molecular cloud which contains massive
star-forming regions that are bright in infrared.  The region also has
abundant molecular and atomic gas traced by CO and HI but also plenty of
dark gas found only by its association with dust emission
\citep{isabelle_dark_gass}. Embedded star-forming regions make it even
more challenging to measure the column density of dust.  Infared and 
${}^{12}\text{CO}$ ($J=1\rightarrow 0$)
contours are overlaid on Figure~\ref{1FGL_J1628.6-2419c} and show good
spatial correlation with the \gev emission \citep{iras_rho_ophiuci,co_rho_ophiuci}.
This source might 
represent $\gamma$-ray emission from the interactions of cosmic rays with
interstellar gas which has not been accounted for in the LAT diffuse
emission model.

@@

Many of the \tev detected extended sources now seen at \gev energies are
currently unidentified and further multiwavelength follow-up observations
will be necessary to understand these particle accelerators.  But the
extension of the spectrum of these \tev sources towards lower energies
by LAT observations can help to determine the origin and nature of the
high-energy emission seen from these sources.

>>>>

\begin{abstract}
Spatial extension is an important characteristic for correctly
associating $\gamma$-ray-emitting sources with their counterparts at other wavelengths
and for obtaining an unbiased model of their spectra.  We present a new
method for quantifying the spatial extension of sources detected by the Large
Area Telescope (LAT), the primary science instrument on the {\em \fermi
Gamma-ray Space Telescope} (\fermi).  We perform a series of Monte Carlo
simulations to validate this tool and calculate the LAT threshold for
detecting the spatial extension of sources.  
\newtext{
We then test all sources
in the second \fermi-LAT catalog (2FGL) for extension. 
We report the detection of seven new spatially extended sources.
}
\end{abstract}

@@

A number of astrophysical source classes including supernova remnants
(SNRs), pulsar wind nebulae (PWNe), molecular clouds, normal galaxies,
and galaxy clusters are expected to be spatially resolvable at
\gev energies.  Additionally, dark matter satellites are also hypothesized to
be spatially extended.  The Large Area Telescope
(LAT) on the {\em \fermi Gamma-ray Space Telescope} (\fermi) has
detected seven SNRs which are significantly extended
at \gev energies: 
W51C, W30, 
IC443, W28, W44, RX\,J1713.7$-$3946,
and the Cygnus Loop
\citep{w51c,w30_lat,ic443,w28,w44,rx_j1713_lat,cygnus_loop_lat}. In addition, 
three extended PWN have been detected: MSH\,15$-$52, Vela~X, and
HESS\,J1825$-$137 \citep{msh1552,velax,fermi_hess_j1825}. Two
nearby galaxies, the Large and Small Magellanic Clouds, and one
radio galaxy, Centaurus A, were spatially resolved at \gev energies
\citep{lmc,smc,cen_a_lat}.  A number of additional sources detected
at \gev energies are positionally coincident with sources that exhibit
large enough extension at other wavelengths to be spatially
resolvable by the LAT at \gev energies.

The current generation of air Cherenkov detectors have
made it apparent that many sources can be spatially resolved
at even higher energies.
Most
prominent was a survey of the Galactic plane using the High Energy
Stereoscopic System (H.E.S.S) which reported 14 spatially extended
sources with extensions varying from $\sim0\fdg1$ to $\sim0\fdg25$
\citep{hess_plane_survey}.  In fact, within our Galaxy only very few
sources detected at \tev energies, most notably the $\gamma$-ray binaries
LS\,5039 \citep{HESSLS5039}, LS I+61$-$303 \citep{MAGICLSI, VERITASLSI},
HESS\,J0632+057 \citep{HESS0632}, and the Crab nebula \citep{crab_weekes},
have no detectable extension.  High-energy $\gamma$-rays from
these sources are produced by the decay of $\pi^0$s produced by hadronic
interactions with interstellar matter and by relativistic electrons
due to Inverse Compton (IC) scattering and bremsstrahlung radiation.  
It is plausible that the \gev and
\tev emission from these sources originates from the same population of
high-energy particles and so at least some of these sources should be
detected at \gev energies.  Studying 
these \tev sources at \gev energies would help to
determine the emission mechanisms producing these high energy photons.

@@

Previous analyses of extended LAT sources were performed as dedicated
studies of individual sources so we expect that a systematic scan of
all LAT detected sources could uncover additional spatially extended
sources.  For these reasons, in Section~\ref{analysis_methods_section}
we present a new systematic method for analyzing spatially extended
LAT sources.  In Section~\ref{monte_carlo_validation}, we demonstrate
that this method can be used to test the statistical significance of the
extension of a LAT source and in Section~\ref{extension_sensitivity}
we calculate the LAT detection threshold to resolve the extension
of a source.  In Section~\ref{dual_localization_method}, we
study the ability of the LAT to distinguish between a spatially
extended source and the confusion of nearby point-like sources.
In Section~\ref{test_2lac_sources}, we further demonstrate that our
detection method does not misidentify point-like sources as being
extended by testing the extension of active galactic nuclei (AGN)
believed to be unresolvable.  In Section~\ref{validate_known},
we systematically reanalyze the twelve extended sources included
in 2FGL and in Section~\ref{systematic_errors_on_extension}
we describe a way to estimate systematic errors on the extension of a source.
In Section~\ref{extended_source_search_method}, we
describe a search for new spatially extended LAT sources. Finally,
in Section~\ref{new_ext_srcs_section} we present the detection of the
extension of nine spatially extended sources that were reported in 2FGL
but as being point-like.  Two of these sources have been previously analyzed in
dedicated publications.

@@

\newtext{
A new maximum-likelihood analysis tool has been developed to address the
unique requirements for studying spatially extended sources with the LAT.
It works by maximizing the Poisson likelihood to find the observing counts
given a parametrized spatial and spectral model of the sky.  
Space is
divided into cubes of position and energy using the healpix representation of
the sky \citep{healpix} and the likelihood is maximized over all bins in
a region.
}
The extension of a source can be modeled by a geometric shape
(e.g. a disk or a two-dimensional Gaussian) and the position, extension,
and spectrum of the source can be simultaneously fit.

@@

The approach presented here is based on a second maximum likelihood
fitting package developed in the LAT Collaboration called \pointlike
\citep{first_cat,matthew_kerr_thesis}.  The choice to base the
spatial extension fitting on \pointlike rather than \gtlike was made
due to considerations of computing time.  The \pointlike algorithm was
optimized for speed to handle larger numbers of sources efficiently,
which is important for our catalog scan and for being able
to perform large-scale Monte Carlo simulations to validate the analysis.
Details on the \pointlike package can be
found in \cite{matthew_kerr_thesis}.  We extended the code to allow a
simultaneous fit of the source extension together with the position and
the spectral parameters.

@@

We considered two different models that can be used to model the
surface brightness profile for extended sources, either a 2D Gaussian
profile
\begin{equation}\label{gauss_pdf}
  I_\text{Gaussian}(x,y)=\tfrac{1}{2\pi\sigma^2}\exp\left(-(x^2+y^2)/2\sigma^2\right)
\end{equation}
or a uniform surface brightness profile
\begin{equation}\label{disk_pdf}
  I_\text{disk}(x,y)=
  \begin{cases}
    \frac{1}{\pi\sigma^2} & x^2+y^2\le\sigma^2 \\
    0                      & x^2+y^2>\sigma^2.
  \end{cases}
\end{equation}
Although these shapes are significantly different,
Figure~\ref{compare_disk_gauss} shows that, after convolution with the
LAT PSF, their PDF are similar for a source that has a 0\fdg5 radius
typical of LAT detected extended sources.  To allow a valid comparison
between the Gaussian and the uniform surface brightness morphologies,
we define the source size as the radius containing 68\% of the
intensity ($\rsixeight$).  $\rsixeight_\text{,Gaussian}=1.51\sigma$
and $\rsixeight_\text{,disk}=0.82\sigma$ where $\sigma$ is defined
in Equation~\ref{gauss_pdf} and Equation~\ref{disk_pdf} respectively.
For this example, $\rsixeight=0\fdg5$ so $\sigma_\text{disk}=0.61\degree$
and $\sigma_\text{Gaussian}=0.33\degree$.

@@

It is impossible to discriminate using only LAT data between a
spatially extended source and multiple point-like sources separated by
angular distances comparable to or smaller than the size of the LAT PSF.
To assess the plausibility of source confusion for situations
in which $\tsext>16$, we developed an algorithm in \pointlike to
simultaneously fit the position and spectrum of two point-like sources.

After simultaneously fitting the two positions and two spectra,
we define \tsinc as twice the increase in the log of the likelihood
fitting the region with two point-like sources compared to fitting the
region with one point-like source:
\begin{equation}
  \tsinc=2\log(\likelihood_\text{2pts}/\likelihood_\text{ps}).
\end{equation} 
For the following analysis of LAT data, \tsinc was computed
by fitting the spectra of the two point-like sources in \gtlike using the best fit positions
of the sources found by \pointlike.

@@

We assessed the power of the $\tsext>\tsinc$ test with a Monte Carlo
study.  We simulated one spatially extended source and fit it as both
an extended source and as two point-like sources using \pointlike.
We then simulated two point-like sources and fit them with the same two
hypotheses. By comparing the distribution of \tsinc and \tsext computed by
\pointlike for the two cases, we evaluated how effective the $\tsext>\tsinc$
test is at rejecting cases of source confusion as well as how
likely it is to incorrectly reject that an extended source is spatially
extended.  All sources were simulated using the same time range as in
Section~\ref{extension_sensitivity} against a background 10 times the
isotropic background measured by EGRET, representative of the background
near the Galactic plane.

@@

The distributions also show that for simulated
extended sources with typical
sizes ($\sigma\sim0\fdg5$), one can often obtain almost as large
an increase in likelihood
with two sources as with one extended source ($\tsinc\sim\tsext$).
This is because although
two point-like sources represent an incorrect spatial model, 
the two point-like sources have four additional degrees
of freedom (two spatial and two spectral parameters)
and can therefore easy model
the extended source and statistical fluctuations in the data.
This effect is most pronounced when using photons with energies between 1
\gev and 100 \gev where the PSF is larger.  
On the other hand,
when testing the two simulated point-like sources for extension our test
found that \tsinc was larger than \tsext.
This is because the one additional extension parameter is less able to
model the second source or statistical fluctuations.
From this, we conclude that the $\tsext>\tsinc$ test is 
powerful at discarding cases in which the true emission is derived
from two point-like sources instead of from a spatially extended
source.

@@

To validate our method, we tested LAT sources associated with AGN for
extension.  \gev emission from AGN is believed to originate from the
cores of kiloparsec-scale jets.  Therefore AGN are
not expected to be spatially resolvable by the LAT and provide a good
calibration source to demonstrate that our extension detection method
does not misidentify point-like sources as being extended.  We note that
megaparsec-scale $\gamma$-ray halos around AGNs have been hypothesized
to be resolvable by the LAT \citep{pair_halo_paper}. However, no such
halo has been discovered in the LAT data so far.

@@

We note that the LAT PSF used in this study was determined
empirically by fitting the observed shape of bright AGN (see
Section~\ref{systematic_errors_on_extension}). Finding that the AGN we
test are not extended is not surprising.  This validation analysis is
not suitable to reject any hypotheses about the existence of megaparsec-scale
halos around AGN.

@@

We developed two criteria for estimating systematic errors
on the extension of the sources.
First, we estimated a systematic error due to
uncertainty in our knowledge of the LAT PSF.  
Before launch, the LAT PSF
was determined by detector simulations which were verified in accelerator
beam tests \citep{atwood_LAT_mission}. However, in-flight data revealed
a discrepancy above a few \gev in the PSF compared to the angular
distribution of photons from bright AGN \citep{lat_on_orbit_psf}.
Subsequently, the PSF was fit empirically to bright AGN and this
empirical parameterization is used in the P7\_V6 IRFs.  To account for
our uncertainty in our knowledge of the PSF, we refit our extended source
candidates using the pre-flight Monte Carlo representation of the PSF
and consider the difference in extension found using the two PSFs as a
systematic error on the extension of a source.  The same approach was used
in \cite{ic443}.  At high energies, we believe that our parameterization
of the PSF from bright AGN is substantially better than the Monte Carlo
representation of the PSF so this systematic error is conservative.

@@

We estimated a second systematic error on the extension of a source
due to uncertainty in our model of the Galactic diffuse emission by
using an alternative model which takes as input templates
calculated by
GALPROP\footnote{GALPROP is a software package for calculating the
Galactic $\gamma$-ray emission based on a model of cosmic-ray propagation
in the Galaxy \citep{galprop1998,galprop2011}. 
See also \url{http://galprop.stanford.edu/} for details.} 
but then fits each template locally in
the surrounding region.
The particular GALPROP model that was used as input is described in
the LAT analysis of the isotropic diffuse
emission \citep{isotropic_lat}.  
The intensities of various components
of the Galactic diffuse emission were fitted individually using a
spatial distribution of the intensities within the ROI as predicted by
the model.  We distinguished contributions from cosmic-ray interactions with the
molecular hydrogen, the atomic and ionized hydrogen, residual gas traced
by dust \citep{isabelle_dark_gass}, and the interstellar radiation
field. We further split the contributions from interactions with molecular
and atomic hydrogen to the Galactic diffuse emission according to the
distance from the Galactic center in which they are produced. Hence, we
replaced the standard diffuse emission model by 18 individually fitted
templates to describe individual components of the diffuse emission.
A similar crosscheck was used in an analysis of RX\,J1713.7$-$3946 
by the LAT Collaboration \citep{rx_j1713_lat}.

@@

The best fit position of nearby point-like sources can be influenced by
the extended source and vice versa.  Similarly,
the best fit position of nearby point-like sources in 2FGL can be biased
by systematic errors at lower energies.
Therefore, after selecting the list of background sources, we iteratively
refit the position and spectrum of nearby background sources as well as
the position and extension of the analyzed spatially extended
sources until the overall fit converged globally.  For each extended
source, we will describe the position of any relocalized background
sources.

After obtaining the overall best fit positions and extensions of all
of the sources in the region using \pointlike, we refit the spectral
parameters of the region using \gtlike.  With \gtlike, we obtained a
second measure of \tsext.  We only consider a source to be extended when
both \pointlike and \gtlike agree that $\tsext>16$. 
We further required that $\tsext>16$ using the alternate diffuse
model presented in section~\ref{systematic_errors_on_extension}.
We then replaced the spatially extended source with two point-like
sources and refit the position and spectrum of the
two point-like sources to calculate \tsinc.
We only consider a source to be spatially extended, instead of being
the result of confusion of two point-like sources, if $\tsext>\tsinc$.
As was shown in Section~\ref{dual_localization_method}, this test is
fairly powerful at removing situations in which the emission actually
originates from two distinct point-like sources instead of one spatially
extended source.  On the other hand, it is still possible that improved
observations could resolve additional structure or new sources that we are
currently not sensitive to. Considering the very complicated morphologies
of extended sources observed at other wavelengths and the high density
of possible sources that are expected to emit at \gev energies, it is
likely that in some of these regions further observations will resolve
that the emission is significantly more complicated than the simple
radially-symmetric uniform surface brightness profile that we assume.

@@

This source is in a region of remarkably complicated diffuse emission.
Even though it is $16\degree$ from the Galactic plane, this source is on
top of the core of the Ophiuchus molecular cloud which contains massive
star-forming regions that are bright in infrared.  The region also has
abundant molecular and atomic gas traced by CO and HI and significant 
dark gas found only by its association with dust emission
\citep{isabelle_dark_gass}. Embedded star-forming regions make it even
more challenging to measure the column density of dust.  Infared and 
${}^{12}\text{CO}$ ($J=1\rightarrow 0$)
contours are overlaid on Figure~\ref{1FGL_J1628.6-2419c} and show good
spatial correlation with the \gev emission \citep{iras_rho_ophiuci,co_rho_ophiuci}.
This source might 
represent $\gamma$-ray emission from the interactions of cosmic rays with
interstellar gas which has not been accounted for in the LAT diffuse
emission model.

@@

Many of the \tev detected extended sources now seen at \gev energies
are currently unidentified and further multiwavelength follow-up
observations will be necessary to understand these particle accelerators.
But extending the spectra of these \tev sources towards lower energies
with LAT observations may help to determine the origin and nature of
the high-energy emission.
